Expected Dependency Pair Match:\\ Predicting improvements to {HTER} with expected syntactic structure

### 2009-05-08 mtjournal.tex
put outline of intro, paradigm sections into kluwer tex

\section{Ordinary Text}  
                    % Produces section heading.  Lower-level
                    % sections are begun with similar 
                    % \subsection and \subsubsection commands.

The ends  of words and sentences are marked 
  by   spaces. It  doesn't matter how many 
spaces    you type; one is as good as 100.  The
end of   a line counts as a space.

One   or more   blank lines denote the  end 
of  a paragraph.

Since any number of consecutive spaces are treated like a single
one, the formatting of the input file makes no difference to
      \TeX,         % The \TeX command generates the TeX logo.
but it makes a difference to you.  
When you use
      \LaTeX,       % The \LaTeX command generates the LaTeX logo.
making your input file as easy to read as possible
will be a great help as you write your document and when you
change it.  This sample file shows how you can add comments to
your own input file.

Because printing is different from typewriting, there are a 
number of things that you have to do differently when preparing 
an input file than if you were just typing the document directly.  
Quotation marks like 
       ``this'' 
have to be handled specially, as do quotes within quotes: 
       ``\,`this'                  % \, separates the double and single quote.
    is what I just 
    wrote, not  `that'\,''.

Dashes come in three sizes: an 
       intra-word 
dash, a medium dash for number ranges like 
       1--2, 
and a punctuation 
       dash---like 
this.

A sentence-ending space should be larger than the space between words
within a sentence.  You sometimes have to type special commands in
conjunction with punctuation characters to get this right, as in the
following sentence.
       Gnats, gnus, etc.\    % `\ ' makes an inter-word space.
       all begin with G\@.   % \@ marks end-of-sentence punctuation.
You should check the spaces after periods when reading your output to
make sure you haven't forgotten any special cases.
Generating an ellipsis 
       \ldots\    % `\ ' needed because TeX ignores spaces after 
          % command names like \ldots made from \ + letters.
          %
          % Note how a `%' character causes TeX to ignore the 
          % end of the input line, so these blank lines do not
          % start a new paragraph.
with the right spacing around the periods 
requires a special  command.

\TeX\ interprets some common characters as commands, so you must type
special commands to generate them.  These characters include the
following: 
       \$ \& \% \# \{ and~\}.

In printing, text is emphasized by using an
       {\em italic\/}  % The \/ command produces the tiny extra space that
               % should be added between a slanted and a following
               % unslanted letter.
type style.

\begin{em}
   A long segment of text can also be emphasized in this way.  Text within
   such a segment given additional emphasis 
      with\/ {\em Roman} 
   type.  Italic type loses its ability to emphasize and become simply
   distracting when used excessively.  
\end{em}

It is sometimes necessary to prevent \TeX\ from breaking a line where
it might otherwise do so.  This may be at a space, as between the
``Mr.'' and ``Jones'' in
       ``Mr.~Jones'',        % ~ produces an unbreakable interword space.
or within a word---especially when the word is a symbol like
       \mbox{\em itemnum\/} 
that makes little sense when hyphenated across 
       lines.

\TeX\ is good at typesetting mathematical formulas like
       \( x-3y = 7 \) 
or
       \( a_{1} > x^{2n} / y^{2n} > x' \).
Remember that a letter like
       $x$        % $ ... $  and  \( ... \)  are equivalent
is a formula when it denotes a mathematical symbol, and should
be treated as one.

>>>>

\section{Introduction}

\begin{itemize}
\item evaluation [esp. automatic evaluation]
\item popular current
  measures BLEU, TER

\item challenges - motivate search for better measures

\item other extensions:
  \begin{itemize}
  \item METEOR 
    \begin{itemize}
    \item stemming and synonym tables
    \item tuned but not generally     tuneable
    \end{itemize}
  \item TERp
    \begin{itemize}
    \item development-set tuning by user
    \item stemming and synonym tables
    \item paraphrase tables
    \end{itemize}
  \end{itemize}
\item prior work with (partial) syntactic locality:
  \begin{itemize}
  \item Liu \& Gildea 
  \item Roark et al. Sparseval
  \item Owczarzak et al. 2007
  \end{itemize}

\item Evaluation of evaluation measures
  \begin{itemize}
  \item correlation vs. human fluency/adequacy 
  \item correlation vs. human-in-the-loop measures (HTER)
  \end{itemize}
\item one challenge of metric-evaluation: underlying doc difficulty 
  \begin{itemize}
  \item describe mean-subtraction
  \end{itemize}
\end{itemize}

\section{Experimental paradigm}

Section explains space of measures to explore

\begin{itemize}
\item F-measure over various bags of components of parse tree

  [ Figure describing Sparseval-ish variant ]

\item Listing possible component valences
  \begin{itemize}
  \item dependent + labeled link + head 
  \item outbound only (dependent +
    label)
  \item inbound only (label + head)
  \item word-word (skipping label)
  \end{itemize}
  \begin{itemize}
  \item 1-grams
  \item 2-grams
  \item \ldots{}
  \end{itemize}

  Note: inbound links \& full pairs "overweight" head words; this is
  a good thing.

  [ figure demonstrating F-measure over d+l+h decomposition of toy
  trees ]

\item Tree features may be extracted from a 1-best tree, or from an
  n-best tree list

  \begin{itemize}
  \item  counts are an expectation over the forest
  \item n parameter: how many trees in the forest
  \item gamma parameter for flattening overconfident parse hyps
  \end{itemize}
  note intentional similarities to Owczarzak paper

\item Components in the basic DPM measures combined in various ways:

  \begin{itemize}
  \item combination of precision, recall scores for different
    components (on analogy with BLEU combination), naive assumption:
    all weighted equally

  \item simple F over items of all valences (naive assumption: all
    weighted equally)
  \end{itemize}
\item Tuneable weights:
  \begin{itemize}
  \item recall that TERp has tuneable system over small number of parameters
    \begin{itemize}
    \item insertion weight
    \item deletion weight
    \item substitution weight
    \item synonym weight (motivated with WordNet)
    \end{itemize}
  \item learn weights for separate precision, recall for various
    components
  \end{itemize}

\item Implementation
  \begin{itemize}
  \item Charniak parser
  \item n=1..50
  \item head-finding, with some modifications
  \item label-construction
  \end{itemize}
\end{itemize}
